---
title: "Introductions"
linktitle: "Week 1: Introductions"
menu:
  readings:
    parent: Readings
    weight: 1
output:
  rmarkdown::html_document
type: docs
weight: 2
---

<style>
  .hvr-sweep-to-left {
    display: inline-block;
    vertical-align: middle;
    -webkit-transform: perspective(1px) translateZ(0);
    transform: perspective(1px) translateZ(0);
    box-shadow: 0 0 1px rgba(0, 0, 0, 0);
    position: relative;
    -webkit-transition-property: color;
    transition-property: color;
    -webkit-transition-duration: 0.25s;
    transition-duration: 0.25s;
  }

.hvr-sweep-to-left:before {
  content: "";
  position: absolute;
  z-index: -1;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: #175676;
    -webkit-transform: scaleX(0);
  transform: scaleX(0);
  -webkit-transform-origin: 100% 50%;
  transform-origin: 100% 50%;
  -webkit-transition-property: transform;
  transition-property: transform;
  -webkit-transition-duration: 0.3s;
  transition-duration: 0.3s;
  -webkit-transition-timing-function: ease-out;
  transition-timing-function: ease-out;
}

.hvr-sweep-to-left:hover, .hvr-sweep-to-left:focus, .hvr-sweep-to-left:active {
  color: white;
}

.hvr-sweep-to-left:hover:before, .hvr-sweep-to-left:focus:before, .hvr-sweep-to-left:active:before {
  -webkit-transform: scaleX(1);
  transform: scaleX(1);
}

td, th, tr, table {
    border: 0 !important;
    border-spacing: 0 !important;
    border-color: transparent;
  }
</style>

### Get Some Advice
First things first:
<br>
<br>
<center>
<iframe src="/videos/snoop_syllabus.mp4" width="320" height="480" frameBorder="0">Read the syllabus.</iframe>
</center>
<br>
<br>

### Review Website

Far be it from us to disagree with Snoop, so you should probably go read the [syllabus](/syllabus/) as soon as possible! Additionally look over the other areas on this site: [readings](/readings/), [materials](/materials/), [extras](/extras/), [tasks](/tasks/), [to do list](/due/), and [resources](/resources/) pages for this class.

### Read Something
```{r echo=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
library(fontawesome)
```

```{r eval = TRUE, echo = FALSE, message=FALSE}
unchecked <- as.character(fontawesome::fa("square", fill = "steelblue"))

checked <- as.character(fontawesome::fa("check-square", fill = "steelblue"))

read_schedule <- read_csv("readings.csv",
                          show_col_types = FALSE) %>% 
                  as_tibble() %>%
                  mutate(Required = case_when(
                  Required == "checked" ~ as.character(fontawesome::fa("check-circle", fill = "#428bca", height = "15px")),
                Required == "unchecked" ~ as.character(fontawesome::fa("times-circle", fill = "#d9534f", height = "15px"))
              )) %>%
                  mutate(across(everything(), as.character)) %>%
                    filter(Week == 1) %>% #CHANGE HERE
                    select(-Week) %>%
                  filter_all(any_vars(!is.na(.))) %>% 
                  mutate(
                    across(everything(), ~replace_na(.x, ""))
                  ) %>%
                select_if(~!all(is.na(.))) 
  
```

```{r message=FALSE, warning=FALSE, eval = TRUE, echo = FALSE}
kable(read_schedule, 
      "html", 
      escape = FALSE,
      align = 'lllccccccccc') %>%
  kable_paper(full_width = F) %>%
  column_spec(1, width = "15em") %>%
  column_spec(2, width = "20em") %>%
  column_spec(3, width = "7em") %>%
  column_spec(4, width = "10em") %>%
  column_spec(5, width = "10em") %>%
  column_spec(6, width = "5em") %>%
  row_spec(0:1, extra_css = 'vertical-align: middle !important;', color = "#ffffff", background = "transparent")
```
